Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-02-04 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added content (Anderson 2018, etc.)

\newenvironment{stepenumerate}{\begin{enumerate}[<+->]}{\end{enumerate}}
\newenvironment{stepitemize}{\begin{itemize}[<+->]}{\end{itemize} }
\newenvironment{stepenumeratewithalert}{\begin{enumerate}[<+-| alert@+>]}{\end{enumerate}}
\newenvironment{stepitemizewithalert}{\begin{itemize}[<+-| alert@+>]}{\end{itemize} }
\newenvironment{itemize_3pt}{\itemize\addtolength{\itemsep}{3pt}}{\enditemize}
\newenvironment{enumerate_3pt}{\enumerate\addtolength{\itemsep}{3pt}}{\endenumerate}

@@

@@

\begin{frame}
\frametitle{?}
	\begin{itemize_3pt}
	\item Bloom and van Reenen (2010, 2019): Business practices, motivation \citep{Bloom2010, Bloom2019}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Heterogeneity in Business Practices}
	\begin{itemize_3pt}
	\item Bloom and van Reenen (2010): Heterogeneity \citep{Bloom2010}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{}
	\begin{itemize_3pt}
	\item Bloom and van Reenen (2019): Correlation with productivity \citep{Bloom2019}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Business Practices in Small Firms}
	\begin{itemize_3pt}
	\item McKenzie and Woodruff (2009, 2017): Heterogeneity and predictiveness \citep{McKenzie2009, McKenzie2017}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Business Practices of Small Firms}
	\begin{itemize_3pt}
	\item McKenzie and Woodruff (2009, 2017): Example categories and practices \citep{McKenzie2009, McKenzie2017}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Best Practices for Small Firms}
	\begin{itemize_3pt}
	\item McKenzie and Woodruff (2017): Portable best practices \citep{McKenzie2017}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{History and Prevalence}
	\begin{itemize_3pt}
		\item At least \textcolor{bdf}{USD 1 billion per year} (to 4-5 million beneficiary entrepreneurs; \citet{McKenzie2020})
		\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity
		\item Examples:
		\begin{itemize_3pt}
			\item Start and Improve Your Business (ILO)
			\item Business Edge (IFC)
			\item EMPRETEC Entrepreneurship Training Workshop (UNCTAD)
		\end{itemize_3pt} 
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Typical Training Program}
	Content
	\begin{itemize_3pt}
	%\textcolor{}{}
	\item Training is delivered by 600 local certified trainers and by a pool of approximately 60 international master trainers. All trainers are also entrepreneurs.
	\item Empretec Training Workshops offer different levels of instruction that include:
	\item 6-day courses (48 hours); 32-hour (usually spread over 4 days) for micro-entrepreneurs with low levels of literacy; Interactive coaching based on real business challenges of participants.
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Typical Training Program}
	Delivery 
	\begin{itemize_3pt}
	\item %\textcolor{}{}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Evidence on Impact}
	\begin{itemize_3pt}
	\item First wave (Karlan and Valdivia, 2011, Field, et al., 2010; Bruhn \& Zia, 2013; Bulte et al., 2017; Anderson, Chandy, and Zia, 2018)
					 \citep{Karlan2011} \citep{Field2010} \citep{Bruhn2013} \citep{Bulte2017} \citep{Anderson2018}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Evidence on Impact}
	\begin{itemize_3pt}
	\item Econometric and implementation issues \citep{McKenzie2014}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Evidence on Impact}
	\begin{itemize_3pt}
	\item Recent evaluations (McKenzie, 2020) \citep{McKenzie2020}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Targeted Training}
	Female entrepreneurs
	\begin{itemize_3pt}
		\item Example: Gender and Enterprise Together \citep[GET Ahead, ILO;][]{Bulte2016,McKenziePuerto2020}
		\item ?
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Targeted Training}
	Young entrepreneurs
	\begin{itemize_3pt}
		\item Entrepreneurship programs in school and university
		\item Example: University final year course in Tunisia \citep{Alaref2020}
		\item ?
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Targeted Training}
	\begin{itemize_3pt}
	\item Gazelles
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Specific Domains}
	\begin{itemize_3pt}
	\item \citep{Anderson2018}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Specific Domain}
	\begin{itemize_3pt}
	\item \citep{Anderson2018}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{On-site Consulting}
	\begin{itemize_3pt}
	\item Bloom, et al. (2013); Karlan et al. (2015); Bruhn, Karlan, and Schoar (2019)
	\item Large firms: \citep{Bloom2013}; SMEs: \citep{Bruhn2018}
	\item \citep{Karlan2015} \citep{Bruhn2019}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{On-site Consulting}
	\begin{itemize_3pt}
	\item ?
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Multimedia delivery}
	TV shows
	\begin{itemize_3pt}
	\item Examples: Ruka Juu in Tanzania \citep{Bjorvatn2020} and El Mashroua in Egypt \citep{Barsoum2018}
	\item ?
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Multimedia delivery}
	TV shows
	\begin{itemize_3pt}
	\item Examples: Ruka Juu in Tanzania \citep{Bjorvatn2020} and El Mashroua in Egypt \citep{Barsoum2018}
	\item ?
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Multimedia delivery}
	Text messages
	\begin{itemize_3pt}
	\item \citep{Cole2019} \citep{Acimovic2020}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Complementary Constraints}
	\begin{itemize_3pt}
	\item McKenzie cash JDE paper
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Complementary Constraints}
	\begin{itemize_3pt}
	\item McKenzie cash JDE paper
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Imprecision of Outcome Measures}
	\begin{itemize_3pt}
	\item Confidence Intervals, pic?
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Reliability of Self-reports}
	\begin{itemize_3pt}
	\item Self-reports of aggregate \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Reliability of Self-reports}
	\begin{itemize_3pt}
	\item Disaggregating quantities in self-reports \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Reliability of Self-report}
	\begin{itemize_3pt}
	\item Direct measures \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Sales vs. Profits}
	\begin{itemize_3pt}
	\item  \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Sales vs. Profits}
	\begin{itemize_3pt}
	\item \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{?}
	\begin{itemize_3pt}
	\item 
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{?}
	\begin{itemize_3pt}
	\item 
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Heterogeneity of Impact}
	\begin{itemize_3pt}
	\item Heterogeneity of treatment effects poorly understood across different approaches
	\item Potential constraints are manifold, and likely context-dependent
	\item Some already mentioned in passing:
	\begin{itemize_3pt}
		\item Credit constraints \citep[see, e.g.,][]{} McKenzie cash paper
		\item Gender norms and constraints
		\item Age-related network and knowledge/skill constraints
	\end{itemize_3pt} 
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Education and literacy}
	\begin{itemize_3pt}
	\item Drexler, Fischer \& Schoar (2014) \citep{Drexler2014}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Family Commitments}
	\begin{itemize_3pt}
	\item 
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Identity Concerns}
	\begin{itemize_3pt}
	\item 
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Aspirations}
	\begin{itemize_3pt}
	\item 
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Local Relevance of Best Practices}
	\begin{itemize_3pt}
	\item 
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Rules of Thumb}
	\begin{itemize_3pt}
	\item Drexler, Fischer \& Schoar (2014) \citep{Drexler2014}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Rules of Thumb}
	\begin{itemize_3pt}
	\item \citep{Arraiz2019} \citep{Cole2019}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Entrepreneurial mindset}
	\begin{itemize_3pt}
	\item \citep{Campos2017}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Entrepreneurial mindset}
	\begin{itemize_3pt}
	\item \citep{Alibhai2019} \citep{Ubfal2019}
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Local Knowledge}
	\begin{itemize_3pt}
	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Local Knowledge}
	\begin{itemize_3pt}
	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Local Knowledge}
	\begin{itemize_3pt}
	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Role Models}
	\begin{itemize_3pt}
	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018)
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Role Models}
	\begin{itemize_3pt}
	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Role Models}
	\begin{itemize_3pt}
	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018)
	\vspace{0.1in}
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Takeaways}
	\begin{itemize_3pt}
    \item
   	\vspace{0.10in}
\end{itemize_3pt}
\end{frame}

\begin{frame}
\frametitle{Questions}
	\textcolor{bdf}{Any questions?}
	\begin{itemize_3pt}
	\item[] .. before we move on to our paper?
	\end{itemize_3pt}
\end{frame}

@@

\begin{frame}
\frametitle{Background}
	\begin{itemize_3pt}
	\item Micro and small firms (MSEs) are typically the main \textcolor{bdf}{source of employment} in the developing world
	\item In \textcolor{bdf}{Indonesia}, MSEs represent .. 
	\begin{itemize_3pt}
		\item .. 99\% of all firms
		\item .. 94.5\% of employment
	\end{itemize_3pt} 
	\item Understanding the factors fostering efficiency and growth of MSEs is an important research and policy goal
	\end{itemize_3pt}
\end{frame}

%------------------------------------------------
\begin{frame}
\frametitle{A Growing Focus on Management}
\begin{itemize_3pt}
\item \textcolor{bdf}{Classroom Training}: Field, et al. (2010); Karlan \& Valdivia (2011); Bruhn \& Zia (2013); McKenzie \& Woodruff (2014, 2017); Bulte et al. (2017); Anderson, Chandy \& Zia (2018); Lafortune et al. (2018)
\vspace{0.1in}
\item \textcolor{bdf}{Consulting}: Bloom, et al. (2013); Karlan et al (2015); Bruhn, Karlan \& Schoar (2019)
\vspace{0.1in}

\item \textcolor{bdf}{Mobilizing Peer Knowledge}:
    \begin{itemize_3pt}
    \item Brooks et al. (2018) $\rightarrow$ Local mentors (market information)
    \item Cai \& Szeidl (2018) $\rightarrow$ Business meetings
    \item Abebe et al. (2019) $\rightarrow$ Management experience matching
    \end{itemize_3pt}
    \vspace{0.1in}
\end{itemize_3pt}
\end{frame}

\subsection{Our Approach}
\begin{frame}
\frametitle{Harnessing Cross-Firm Heterogeneity}
Some stylized facts about business practices in small firms
\begin{itemize_3pt}
	\item Vast heterogeneity in business practices and performance across similar businesses \citep{deMel2009}
	\item Variation in practices accounts for more than 20\% of variation in productivity within the same firm in the US \citep{Bloom2019}
	\item[] $\rightarrow$ Research has largely overlooked this heterogeneity in program design and implementation
\end{itemize_3pt}

@@

Our idea is to \textcolor{bdf}{make productice use of this heterogeneity} in research design: 
\begin{itemize_3pt}
	\item Use cross-firm variation to identify \textcolor{bdf}{practices associated with business performance}
	\item \textcolor{bdf}{Curate local best practices}
	\item Test different \textcolor{bdf}{modes of delivery}, and their cost-effectiveness
\end{itemize_3pt}

@@

	\end{table}}}
\begin{itemize_3pt}
\item Test of Joint Orthoganality from Multinomial Logit (P-value): 0.857
\end{itemize_3pt}
\end{frame}

>>>>

\newenvironment{stepenumerate}{\begin{enumerate}[<+->]}{\end{enumerate}}
\newenvironment{stepitemize}{\begin{itemize}[<+->]}{\end{itemize} }
\newenvironment{stepenumeratewithalert}{\begin{enumerate}[<+-| alert@+>]}{\end{enumerate}}
\newenvironment{stepitemizewithalert}{\begin{itemize}[<+-| alert@+>]}{\end{itemize} }
\newenvironment{itemize_2pt}{\itemize\addtolength{\itemsep}{2pt}}{\enditemize}
\newenvironment{enumerate_2pt}{\enumerate\addtolength{\itemsep}{2pt}}{\endenumerate}

@@

% Create subsection transitions without subsection numbering
\def\subsectionname{\translate{Subsection}}
\def\insertsubsectionnumber{\arabic{subsection}}
\setbeamertemplate{subsection page}
{
  %\begin{centering}
    %{\usebeamerfont{subsection name}\usebeamercolor[fg]{subsection name}\subsectionname~\insertsubsectionnumber}
    %\vskip1em\par
    \begin{beamercolorbox}[sep=14pt,center]{part title}
      \setbeamerfont{subsection title}{size=\fontsize{14}{20}\selectfont}
      \usebeamerfont{subsection title}\insertsubsection\par
    \end{beamercolorbox}
  %\end{centering}
}
\def\subsectionpage{\usebeamertemplate*{subsection page}}
\AtBeginSubsection
{\frame{\subsectionpage}}

@@

\begin{frame}
\frametitle{?}
	\begin{itemize_2pt}
	\item Bloom and van Reenen (2010, 2019): Business practices, motivation \citep{Bloom2010, Bloom2019}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Heterogeneity in Business Practices}
	\begin{itemize_2pt}
	\item Bloom and van Reenen (2010): Heterogeneity \citep{Bloom2010}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{}
	\begin{itemize_2pt}
	\item Bloom and van Reenen (2019): Correlation with productivity \citep{Bloom2019}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Business Practices in Small Firms}

	Vast heterogeneity in business practices \textcolor{bdf}{also among small firms} \citep{McKenzie2009, McKenzie2017}..
	\begin{itemize_2pt}
		\item .. between countries
		\item .. between industries
		\item .. between firms
	\end{itemize_2pt}

	\vspace{0.5em}

	In cross-section, business practices \textcolor{bdf}{associated with higher sales and profits} \citep{McKenzie2017}

\begin{frame}
\frametitle{Business Practices of Small Firms}

	\citet{McKenzie2017} identify \textcolor{bdf}{set of XX best practices} most closely associated with business performance
	\begin{itemize_2pt}
		\item 5 major domains of practices
		\begin{enumerate_2pt}
			\item Book-keeping
			\item ?
			\item ?
			\item Inventory management and stock control
			\item Marketing
		\end{enumerate_2pt}
	\item[] $\rightarrow$ Association with performance robust across industries and countries
	\item[] $\rightarrow$
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Business Practices of Small Firms}
	\citet{McKenzie2017} identify set of XX practices most closely associated with business performance
	\begin{itemize_2pt}
		\item Example practices:
		\begin{itemize_2pt}
			\item 
			\item 
			\item 
			\item 
			\item 
		\end{itemize_2pt}
	\item Does adoption of "best practices" \emph{cause} increase in performance?
	\item How can practice adoption best be facilitated?
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{History and Prevalence}
	\begin{itemize_2pt}
		\item At least \textcolor{bdf}{USD 1 billion per year} (to 4-5 million beneficiary entrepreneurs; \citet{McKenzie2020})
		\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity
		\item Examples:
		\begin{itemize_2pt}
			\item Start and Improve Your Business (ILO)
			\item Business Edge (IFC)
			\item EMPRETEC Entrepreneurship Training Workshop (UNCTAD)
		\end{itemize_2pt} 
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Typical Training Program}
	Content
	\begin{itemize_2pt}
	%\textcolor{}{}
	\item Training is delivered by 600 local certified trainers and by a pool of approximately 60 international master trainers. All trainers are also entrepreneurs.
	\item Empretec Training Workshops offer different levels of instruction that include:
	\item 6-day courses (48 hours); 32-hour (usually spread over 4 days) for micro-entrepreneurs with low levels of literacy; Interactive coaching based on real business challenges of participants.
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Typical Training Program}
	Delivery 
	\begin{itemize_2pt}
	\item %\textcolor{}{}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Evidence on Impact}
	\begin{itemize_2pt}
	\item First wave (Karlan and Valdivia, 2011, Field, et al., 2010; Bruhn \& Zia, 2013; Bulte et al., 2017; Anderson, Chandy, and Zia, 2018)
					 \citep{Karlan2011} \citep{Field2010} \citep{Bruhn2013} \citep{Bulte2017} \citep{Anderson2018}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Evidence on Impact}
	\begin{itemize_2pt}
	\item Econometric and implementation issues \citep{McKenzie2014}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Evidence on Impact}
	\begin{itemize_2pt}
	\item Recent evaluations (McKenzie, 2020) \citep{McKenzie2020}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Targeting Training}
	Female entrepreneurs
	\begin{itemize_2pt}
		\item \textcolor{bdf}{Most common type of targeted training} (potentially complementary to classical microfinance model)
		\item Example: Gender and Enterprise Together \citep[GET Ahead, ILO;][]{Bulte2016,McKenziePuerto2020}
		\item ?
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Targeting Training}
	Young entrepreneurs
	\begin{itemize_2pt}
		\item Typically embedded as entrepreneurship programs in school and university
		\item Example: University final year course in Tunisia \citep{Alaref2020}
		\begin{itemize_2pt}
			\item
			\item
		\end{itemize_2pt}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Targeting Training}
	High-growth businesses ("gazelles")
	\begin{itemize_2pt}
	\item
	\item
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Training Specific Domains}

	\citet{Anderson2018} assign 852 South African businesses to two distinct trainings:
	\begin{enumerate_2pt}
		\item Finance/accounting skills
		\item Marketing/sales skills
	\end{enumerate_2pt}

\begin{frame}
\frametitle{Training Specific Domains}

	\citet{Anderson2018} assign 852 South African businesses to two distinct trainings:
	\begin{enumerate_2pt}
		\item Finance/accounting skills
		\begin{itemize_2pt}
			\item Increased profits
			\item "Efficiency focus" on lower costs
			\item[] $\rightarrow$ Benefits established businesses (less market exposure)
		\end{itemize_2pt}
		\item Marketing/sales skills
		\begin{itemize_2pt}
			\item Increased profits
			\item "Growth focus" on higher sales, stock investments, and hiring
			\item[] $\rightarrow$ Benefits new businesses (less market exposure)
		\end{itemize_2pt}
	\end{enumerate_2pt}

\begin{frame}
\frametitle{Training Specific Domain}
	\begin{itemize_2pt}
	\item \citep{Anderson2018}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{On-site Consulting}
	\begin{itemize_2pt}
	\item Bloom, et al. (2013); Karlan et al. (2015); Bruhn, Karlan, and Schoar (2019)
	\item Large firms: \citep{Bloom2013}; SMEs: \citep{Bruhn2018}
	\item \citep{Karlan2015} \citep{Bruhn2019}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{On-site Consulting}
	\begin{itemize_2pt}
	\item ?
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Multimedia delivery}
	TV shows
	\begin{itemize_2pt}
	\item Examples: Ruka Juu in Tanzania \citep{Bjorvatn2020} and El Mashroua in Egypt \citep{Barsoum2018}
	\item ?
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Multimedia delivery}
	TV shows
	\begin{itemize_2pt}
	\item Examples: Ruka Juu in Tanzania \citep{Bjorvatn2020} and El Mashroua in Egypt \citep{Barsoum2018}
	\item ?
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Multimedia delivery}
	Text messages
	\begin{itemize_2pt}
	\item \citep{Cole2019} \citep{Acimovic2020}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Complementary Constraints}
	\begin{itemize_2pt}
	\item McKenzie cash JDE paper
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Complementary Constraints}
	\begin{itemize_2pt}
	\item McKenzie cash JDE paper
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Imprecision of Outcome Measures}
	\begin{itemize_2pt}
	\item Confidence Intervals, pic?
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Reliability of Self-reports}
	\begin{itemize_2pt}
	\item Self-reports of aggregate \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Reliability of Self-reports}
	\begin{itemize_2pt}
	\item Disaggregating quantities in self-reports \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Reliability of Self-report}
	\begin{itemize_2pt}
	\item Direct measures \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Sales vs. Profits}
	\begin{itemize_2pt}
	\item  \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Sales vs. Profits}
	\begin{itemize_2pt}
	\item \citep{deMel2009}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{?}
	\begin{itemize_2pt}
	\item 
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{?}
	\begin{itemize_2pt}
	\item 
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Heterogeneity of Impact}
	\begin{itemize_2pt}
	\item Heterogeneity of treatment effects poorly understood across different approaches
	\item Potential constraints are manifold, and likely context-dependent
	\item Some already mentioned in passing:
	\begin{itemize_2pt}
		\item Credit constraints \citep[see, e.g.,][]{} McKenzie cash paper
		\item Gender norms and constraints
		\item Age-related network and knowledge/skill constraints
	\end{itemize_2pt} 
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Education and literacy}
	\begin{itemize_2pt}
	\item Drexler, Fischer \& Schoar (2014) \citep{Drexler2014}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Family Commitments}
	\begin{itemize_2pt}
	\item 
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Identity Concerns}
	\begin{itemize_2pt}
	\item 
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Aspirations}
	\begin{itemize_2pt}
	\item 
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Local Relevance of Best Practices}
	\begin{itemize_2pt}
	\item 
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Rules of Thumb}
	\begin{itemize_2pt}
	\item Drexler, Fischer \& Schoar (2014) \citep{Drexler2014}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Rules of Thumb}
	\begin{itemize_2pt}
	\item \citep{Arraiz2019} \citep{Cole2019}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Entrepreneurial mindset}
	\begin{itemize_2pt}
	\item \citep{Campos2017}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Entrepreneurial mindset}
	\begin{itemize_2pt}
	\item \citep{Alibhai2019} \citep{Ubfal2019}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Local Knowledge}
	\begin{itemize_2pt}
	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Local Knowledge}
	\begin{itemize_2pt}
	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Local Knowledge}
	\begin{itemize_2pt}
	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Role Models}
	\begin{itemize_2pt}
	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018)
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Role Models}
	\begin{itemize_2pt}
	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Role Models}
	\begin{itemize_2pt}
	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018)
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Takeaways}
	\begin{itemize_2pt}
    \item
   	\vspace{0.10in}
\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Questions}
	\textcolor{bdf}{Any questions?}
	\begin{itemize_2pt}
	\item[] .. before we move on to our paper?
	\end{itemize_2pt}
\end{frame}

@@

\begin{frame}
\frametitle{Background}
	\begin{itemize_2pt}
	\item Micro and small firms (MSEs) are typically the main \textcolor{bdf}{source of employment} in the developing world
	\item In \textcolor{bdf}{Indonesia}, MSEs represent .. 
	\begin{itemize_2pt}
		\item .. 99\% of all firms
		\item .. 94.5\% of employment
	\end{itemize_2pt} 
	\item Understanding the factors fostering efficiency and growth of MSEs is an important research and policy goal
	\end{itemize_2pt}
\end{frame}

%------------------------------------------------
\begin{frame}
\frametitle{A Growing Focus on Management}
\begin{itemize_2pt}
\item \textcolor{bdf}{Classroom Training}: Field, et al. (2010); Karlan \& Valdivia (2011); Bruhn \& Zia (2013); McKenzie \& Woodruff (2014, 2017); Bulte et al. (2017); Anderson, Chandy \& Zia (2018); Lafortune et al. (2018)
\vspace{0.1in}
\item \textcolor{bdf}{Consulting}: Bloom, et al. (2013); Karlan et al (2015); Bruhn, Karlan \& Schoar (2019)
\vspace{0.1in}

\item \textcolor{bdf}{Mobilizing Peer Knowledge}:
    \begin{itemize_2pt}
    \item Brooks et al. (2018) $\rightarrow$ Local mentors (market information)
    \item Cai \& Szeidl (2018) $\rightarrow$ Business meetings
    \item Abebe et al. (2019) $\rightarrow$ Management experience matching
    \end{itemize_2pt}
    \vspace{0.1in}
\end{itemize_2pt}
\end{frame}

\subsection{Our Approach}
\begin{frame}
\frametitle{Harnessing Cross-Firm Heterogeneity}
Some stylized facts about business practices in small firms
\begin{itemize_2pt}
	\item Vast heterogeneity in business practices and performance across similar businesses \citep{deMel2009}
	\item Variation in practices accounts for more than 20\% of variation in productivity within the same firm in the US \citep{Bloom2019}
	\item[] $\rightarrow$ Research has largely overlooked this heterogeneity in program design and implementation
\end{itemize_2pt}

@@

We \textcolor{bdf}{make productive use of this heterogeneity} in our research design: 
\begin{itemize_2pt}
	\item Use cross-firm variation to identify \textcolor{bdf}{practices associated with business performance}
	\item \textcolor{bdf}{Curation} of local best practices
	\item Test different \textcolor{bdf}{modes of delivery}, and their cost-effectiveness
\end{itemize_2pt}

@@

	\end{table}}}
\begin{itemize_2pt}
\item Test of Joint Orthoganality from Multinomial Logit (P-value): 0.857
\end{itemize_2pt}
\end{frame}
